manuscript

### 2023-11-30 scripts/manuscript.qmd

---
title: "manuscript"
format: pdf
editor: visual
author: "Leah Peterson, Alexus Rock, and Ben Pfingston"
bibliography: biblio.bib
warning : false
message : false
echo : false
---

>>>>

---
title: "manuscript"
format: pdf
editor: visual
author: "Leah Peterson, Alexus Rock, and Ben Pfingston"
bibliography: biblio.bib
warning : false
message : false
echo : false
---
```{r}
# Hi! Danielle here. Your code looks so clean! It is super easy to follow.
# All of your data and figures loaded properly too. Great job!
# I have never seen the "scale_x_discrete" code before so I definitely learned that from your code.
# I really appreciated how you left a note in your code explaining the new labels/why you labeled something the way you did for your collaborators. Super helpful!
# I noticed that you labeled all the code chunks with box plots so I made a label from your code chunk for the scatter plot following the same format - "scatterplot-ss-score-ppis-total"
```
